---
title: "Home"
author: "Derek, Eric, Edward, Nuo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(ggplot2)
setwd('C:/Users/chenn/Documents/Info498F/Final-Project-X/shiny-app')
source('scripts/summary-info.r')





```

Welcome!
========

For the final project, we decided to create a visualization that accurately reflects the college admission statistics of over 7000 private/public universities throughout the United States. In addition, we have analyzed the dataset as a whole and produced a state-level report based on our findings. This project is made interactive using `Shiny`, viewers can interact with the map and the graphs to understand the dataset from a different perspective by changing the corresponding inputs.



## Overview
Below is a table that ...

```{r, echo=FALSE, results='asis'}
knitr::kable(data_by_state, align = NULL)
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 


```{r, echo=FALSE}
#```{r, fig.show='hold'}

names(data_by_state)[names(data_by_state) == 'Average SAT Score'] <- 'SAT'

names(data_by_state)[names(data_by_state) == 'Average Acceptance Rate'] <- 'ADM_RATE'

data_by_state$ ADM_RATE <- as.numeric(sub("%", "", data_by_state$ ADM_RATE))

# names(data_by_state)[names(data_by_state) == ''] <- ''

plot_ly(data_by_state, x = SAT, y = ADM_RATE, text = STABBR,
        mode = "markers", color = ADM_RATE, size = ADM_RATE/1000 )


```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.