---
title: "Home"
author: "Derek, Eric, Edward, Nuo"
date: "`r Sys.Date()`"
output: html_document

---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(ggplot2)
setwd('C:/Users/chenn/Documents/Info498F/Final-Project-X/shiny-app')
source('scripts/summary-info.r')


```

Welcome!
========

For the final project, we decided to create a visualization that accurately reflects the college admission statistics of over 7000 private/public universities throughout the United States. In addition, we have analyzed the dataset as a whole and produced a state-level report based on our findings. This project is made interactive using `Shiny`, viewers can interact with the map and the graphs to understand the dataset from a different perspective by changing the corresponding inputs.

## Who?

This application is geared toward 



## Overview
Below is a table that ...

```{r, echo=FALSE, results='asis'}
names(data_by_state)[names(data_by_state) == 'STABBR'] <- 'State'
knitr::kable(data_by_state, align = NULL)
```


## Score Conversion 

```{r, echo=FALSE}
names(score_chart)[names(score_chart) == 'New.SAT..starting.March.2016.'] <- 'New SAT Score'
names(score_chart)[names(score_chart) == 'Old.SAT..before.March.2016.'] <- 'Old SAT Score'

knitr::kable(score_chart, align = NULL)

```
