---
title: "Home"
author: "Derek, Eric, Edward, Nuo"
date: "`r Sys.Date()`"
output: html_document

---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(ggplot2)
setwd('C:/Users/chenn/Documents/Info498F/Final-Project-X/shiny-app')
source('scripts/summary-info.r')


```

Welcome!
========

For the final project, we decided to create a visualization that accurately reflects the college admission statistics of over 7000 private/public universities throughout the United States. In addition, we have analyzed the dataset as a whole and put together an interactive platform that filters down the list of schools based on your test scores and area of interest. This project is made interactive using `Shiny`, viewers can interact with the map and the graphs to understand the dataset from a different perspective by changing the corresponding inputs.

# Introduction

> On March 5, 2014, College Board announced that a redesigned version of the SAT would be administered for the first time in 2016. The exam will revert to the 1600-point scale, the essay will be optional, and students will have three hours to take the exam plus 50 additional minutes to complete the essay. 

This application is created to assist future generations of test takers who are struggling to apply for college. Instead of spending hours of time randomly searching on internet for a slim chance to find the right fit for you, this application enables you to come up with a list of universities that you are likely to get in based on your test scores and region of interest.  


## Overview
Below is a table that ...

```{r, echo=FALSE, results='asis'}
names(data_by_state)[names(data_by_state) == 'STABBR'] <- 'State'
knitr::kable(data_by_state, align = NULL)
```


## Score Conversion 

```{r, echo=FALSE}
names(score_chart)[names(score_chart) == 'New.SAT..starting.March.2016.'] <- 'New SAT Score'
names(score_chart)[names(score_chart) == 'Old.SAT..before.March.2016.'] <- 'Old SAT Score'

knitr::kable(score_chart, align = NULL)

```
